### 2020-06-16 Documents/ESA/sections/ResearchTimeline.tex
Included ESA, updated Write Up
Updated ESA

\begin{document}
    \section{Chaotic Dynamics in MARL} \label{sec::Chaos_in_MARL}
    \section{Large Agent Dynamics} \label{sec::Large_Agent_Dynamics}
    \section{Swarm Control through Fields} \label{sec::Swarm_Field_Control}
    \section{Incorporation of Intelligence in Control} \label{sec::Intelligence_in_control}
\end{document}

>>>>

\begin{document}

	This chapter outlines a tentative timeline of the research described thus far. The numbers in
	brackets denote the estimated months of the PhD that these are likely to take place with zero
	being the beginning of the PhD (October 2019) and 48 marking the end (September 2023). Note that
	there is a period of six months at the end which exists to allow for a margin of error.

	\begin{enumerate}
		\item Characterisation of Complex Dynamics in Reinforcement Learning Games (\textbf{9 - 12})
		\begin{itemize}
			\item Determining and plotting a simplified expression for a stability line general
			p-player games using Q-Learning (\textbf{9 - 10}).
			\item Running large scale simulations of Q-Learning games to experimentally verify
			results. (\textbf{9 - 11}).
			\item Characterising the Lyapunov exponent for modes of unstable behaviour in Q-Learning
			Dynamics (\textbf{11 - 14})
		\end{itemize}

		\item Control of Swarms with Independent Agents (\textbf{11 - 18})
		\begin{itemize}
			\item Setting up a model predictive control problem for the reduced assumptions of
			particles with no (or limited) interactions (\textbf{11 - 12}) and solving the resulting
			optimisation problem (\textbf{12 - 18}). 
			\item Designing and running simulation code. (\textbf{15 - 18})
		\end{itemize}

		\item Characterisation of the Learning Dynamics of Co-operative Mean Field Games (\textbf{11
				- 18})
		\begin{itemize}
			\item Evaluating the stability of co-operative ($\Gamma = 1$) mean-field games (\textbf{11 - 13})
			\item Evaluating the Lyapunov exponent of the unstable behaviour (\textbf{13 - 16})
			\item Running large scale simulations to verify results (\textbf{15 - 18})
		\end{itemize}

		\item Control of Interacting Swarming Agents (\textbf{19 - 30})
		\begin{itemize}
			\item Setting up and solving MPC optimisation problem on the collisional Vlasov
			equation with short-range interactions between agents. (\textbf{19 - 25})
			\item Designing and running simulation code. (\textbf{24 - 30})
		\end{itemize}

		\item Control of Co-operative Intelligent Swarming Agents (\textbf{28 - 34})
		\begin{itemize}
			\item Setting up and solving MPC optimisation problem on the collisional Vlasov
			equation with augmented interaction term constrained on learning dynamics. (\textbf{28 -
			33})
			\item Designing and running simulation code. (\textbf{32 - 37})
		\end{itemize}

		\item Thesis Completion (\textbf{34 - 42})
		\begin{itemize}
			\item Writing Up (\textbf{34 - 38})
			\item Proof Reading and Editing (\textbf{39 - 41})
			\item PhD Completion (\textbf{41 - 42})
		\end{itemize}

	\end{enumerate}

\end{document}

### 2020-06-16 Documents/ESA/sections/ShortTermGoals.tex
Updated ESA

    \subsection{Research Summary} % \subfile{./sections/ResearchSummary.tex} \label{sec::Research
    % Summary}

@@

    This section builds on the work described in \ref{sec::Swarm_Field_Control} and will be the next
    mode of inquiry upon the completion of the work described in \ref{sec::Chaos_in_Q-Learning}.
    Recall that Bellomo et al describe the evolution of the distribution of a 'collisionless' swarm
    through

    \begin{equation}
    \begin{align*}    
        \partial_t f + \Vec{v} \cdot \nabla_{\Vec{x}} f + \kappa \nabla_{\Vec{v}} \cdot (F_a (f) f)
        = 0 \quad  (\Vec{x}, \Vec{v}) \in \Omega[f] \times D_{\Vec{v}}, \quad t>0, \\
        F_a[f](t, \Vec{x}, \Vec{v}) = - \int_{\Omega [f] \times D_{\Vec{v}}} \psi (|\Vec{x} - \Vec
        {x^*}|)(\Vec{v} - \Vec{x^*}) f(t, \Vec{x}^*, \Vec{v}^*) d\Vec{x}^* d\Vec{v}^*.
    \end{align*}
    \end{equation}

    In this study we will attempt to formulate an optimal control problem in which the term $F_a[f]
    (t, \Vec{x}, \Vec{v})$ takes the role of the control input (we will likely choose a fixed value
    of $\psi$ to reduce complexity). Note that $F_a$ is dependent on the density function f and so
    we aim to apply feedback controls to the swarm.

>>>>

    \subsection{Research Summary} %\subfile{./sections/ResearchSummary.tex} \label{sec::Research
    % Summary}

@@

    This section builds on the work described in \ref{sec::Swarm_Field_Control} and will be the next
    mode of inquiry upon the completion \ref{sec::Chaos_in_Q-Learning}.
    Bellomo et al describe the evolution of the distribution of a 'collisionless' swarm
    through

    \begin{equation*}
    \begin{split}    
        \partial_t f + \Vec{v} \cdot \nabla_{\Vec{x}} f + \kappa \nabla_{\Vec{v}} \cdot (F_a (f) f)
        = 0 \quad  (\Vec{x}, \Vec{v}) \in \Omega[f] \times D_{\Vec{v}}, \quad t>0, \\
        F_a[f](t, \Vec{x}, \Vec{v}) = - \int_{\Omega [f] \times D_{\Vec{v}}} \psi (|\Vec{x} - \Vec
        {x^*}|)(\Vec{v} - \Vec{x^*}) f(t, \Vec{x}^*, \Vec{v}^*) d\Vec{x}^* d\Vec{v}^*, 
    \end{split}
    \end{equation*}

    in which $f = f(t, \Vec{x}, \Vec{v})$ is the one-particle probability density function at
    phase-space position ($\Vec{x}, \Vec{v}$), $\Vec{v}$ and time $t$. $\kappa \geq 0$ is a scalar
    coefficient, $\psi$ denotes the communication strength between particles, and ($\Vec{x}^*, \Vec
    {v}^*$) gives the position in phase space of a 'field particle'.

    In this study we will attempt to formulate an model predictive control problem in which the term
    $F_a[f] (t, \Vec{x}, \Vec{v})$ takes the role of the control input (we will likely choose a
    fixed value of $\psi$ to reduce complexity). The process will be inspired from the works of
    Burger et al. \cite{Berger2019} and Borzi et al. \cite{Borzi2014} However, we will aim to
    control the behaviour of the system through interactions with 'field particles' (determined by
    $F_a[f]$) rather than through the leader-follower interactions posed by the aforementioned
    studies. We will illustrate the effectiveness of the results through 2D numerical simulation. It
    will be interesting to perform a similar analysis to Ko and Zuazua \cite{Ko2019} in which the
    cost functional is altered to favour particular metrics  (e.g. running cost, control time etc.)
    and also analyse the effect of varying the time horizon.
